\documentclass[a4paper,12pt]{article}
\usepackage[a4paper,margin=0.5cm]{geometry}
\geometry{paperheight=60cm}
% \usepackage[margin=0.5cm]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage[none]{hyphenat}

\pagenumbering{gobble} % no page numbers

% Customize section fonts
\titleformat{\section}{\large\bfseries\uppercase}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}


% Custom Commands
\newcommand{\linuxGitHub}{\href{https://github.com/karan51ngh/karan51ngh}{Linux}}
\newcommand{\gitGitHub}{\href{https://github.com/karan51ngh/gitCheatSheet}{Git}}
\newcommand{\jsGitHub}{\href{https://github.com/karan51ngh?tab=repositories&q=&type=&language=javascript}{JavaScript}}
\newcommand{\cppGitHub}{\href{https://github.com/karan51ngh/topicWiseQuestions}{C++}}
\newcommand{\pythonGitHub}{\href{https://github.com/karan51ngh?tab=repositories&q=&type=&language=python}{Python}}
\newcommand{\praw}{\href{https://github.com/praw-dev/praw}{PRAW (Python Reddit API Wrapper)}}
\newcommand{\MachineLearning}{\href{https://github.com/karan51ngh/machineLearning}{Machine Learning}}
\newcommand{\Java}{\href{https://github.com/karan51ngh/javaprogramming}{Java}}

\begin{document}

\begin{center}
  {\LARGE \textbf{Karan Singh Bagga}} \\
  
  \faEnvelope\ \href{mailto:karansingh9535@gmail.com}{karansingh9535@gmail.com} | 
  \faGithub\ \href{https://github.com/karan51ngh}{github.com/karan51ngh} \\ 
  \faLinkedin\ \href{https://linkedin.com/in/karan51ngh}{linkedin.com/in/karan51ngh} |
  \faMedium\ \href{https://medium.com/@karan51ngh}{medium.com/@karan51ngh}
  \\
  \vspace{0.8em}
  React \& Java Developer with 2 years’ experience building enterprise applications. Delivered end-to-end UI and backend features, including secure APIs and AI-powered modules.
\end{center}

% \vspace{1em}

% ========================
% \section*{\faToolsSkills}
\section*{Skills}
\textbf{Languages:} \cppGitHub, \Java, \jsGitHub, TypeScript, \pythonGitHub \\
\textbf{Frontend:} React (React.js), HTML, CSS \\
\textbf{Backend:} Spring Boot, REST APIs, SQL, Node.js\\
\textbf {Artificial Intelligence:} \MachineLearning, LLM and Prompt Engineering \\
\textbf{Tools:} \linuxGitHub, \gitGitHub, Postman \\
\textbf{Software Development:} GitHub / GitLab, Agile, Jira

% ========================
% \section*{\faBriefcase\hspace{0.5em}Experience}
\section*{Experience}
\subsection*{\textbf{Oracle}}

\textbf{Associate Software Developer} \hfill \textit{Hyderabad | Hybrid, Aug 2023 -- Present}
\begin{itemize}[leftmargin=1.5em]
  \item Engineered the User Interface and API integration handlers for a new single-page web application: \textbf{Enterprise Management System}, by Oracle Hospitality, using React.js and TypeScript.
        \begin{itemize} 
            \item Delivered the entire UI from inception to production over \textbf{1.5 years} as a key member of a \textbf{2-person team}.
            \item Successfully launched the application, leading to the onboarding of \textbf{5 pilot customers}.
        \end{itemize}
  \item Developed \textbf{7} secure \textbf{RESTful APIs} for \textbf{Enterprise Management System} using \textbf{Java} and \textbf{Spring Boot}, implementing access control to protect customer data and ensuring seamless integration with frontend applications.
  \item Spearheaded the end-to-end development and deployment of \textbf{2 AI}-powered features: an automated text translation tool and a chatbot assistant.
        \begin{itemize} 
            \item Leveraged \textbf{Large Language Model (LLM)} engineering to build and integrate the AI functionalities within \textbf{Enterprise Management System}.
            \item Improved the user workflow by automating text translation, a change that \textbf{80\% of customers} confirmed increased their convenience.
        \end{itemize}
\end{itemize}

\subsection*{\textbf{Oracle}}
\textbf{Software Development Intern} \hfill \textit{Remote, Jan 2023 -- Jul 2023}
\begin{itemize}[leftmargin=1.5em]
  \item Upgraded the \textbf{Linux} OS Version across \textbf{300+ developer VMs} to standardize environments and strengthen security compliance, unlocking access to newer tools and increasing developer productivity.
  \item Rectified \textbf{3 open issues} in the custom logger for the \textbf{OPERA Cloud} REST API wrapper, delivering more accurate and clear log outputs to accelerate developer debugging and system monitoring.
\end{itemize}

% ========================
% \section*{\faRocket\hspace{0.5em}Projects}
\section*{Projects}
\subsection*{BetterPrompt} \textit{\href{https://github.com/BtrPrmt/BetterPrompt-extension}{Frontend Source Code}} | \textit{\href{https://github.com/BtrPrmt/BetterPrompt-WS}{Backend Source Code}} \\
\textit{"BetterPrompt"} is a Browser extension designed to enhance the quality of prompts written for Large Language Model (\textbf{LLM}) services such as ChatGPT, Grok, Perplexity.AI etc.
\begin{itemize}[leftmargin=1.5em]
    \item It currently consists of \textbf{2 features}: Modifying and Rating the user-written prompts in real-time to improve prompt clarity, specificity, and overall effectiveness.
    \item Harnessed \textbf{JavaScript} and \textbf{Chrome extension APIs} to build the extension Frontend which consisted of \textbf{2 buttons} and several helper methods. 
    \item Used \textbf{Node.js} to implement \textbf{3 web-services} in the Backend to leverage the \textbf{GPT} and \textbf{Llama} LLM models.  
    \item Engineered and wrote \textbf{5 distinct Prompts} to utilize \textbf{GPT} and \textbf{Llama} LLM models for prompt improvement and prompt rating calculation.
\end{itemize}
\subsection*{MediChain} \textit{\href{https://github.com/karan51ngh/MediChain}{Source Code}} | \textit{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4804243}{Paper Link}} \\
\textit{"MediChain"} is a proof-of-concept (\textbf{POC}) implementation of the published paper titled: \textit{"Proof-of-Trust-in-Expertise (PoTE): A Consensus Mechanism for Healthcare based Consortium Blockchains"}.
\begin{itemize}[leftmargin=1.5em]
    \item It is architected as a Consortium \textbf{Blockchain} for Seamless Patient Information Management in National Healthcare.
    \item Leveraged \textbf{Python} along with \textbf{7 standard libraries} such as \textbf{socket}, \textbf{sqlite3}, \textbf{threading}, \textbf{hashlib} etc., utilizing core CS concepts like networking, cryptography, and concurrent programming to craft the POC.
    \item Built the \textbf{Blockchain} and the \textbf{Mining Process} from scratch, utilizing \textbf{SHA-256} hashing.
    \item Designed a modified version of \textbf{Proof of Stake (PoS)} to mimic \textbf{Proof of Trust in Expertise (PoTE)}.
\end{itemize}
\subsection*{RedditRefresh} \textit{\href{https://github.com/karan51ngh/RedditRefresh}{Source Code}} \\
\textit{"RedditRefresh"} is a Python Script that helps you with \textbf{4 Operations}: Bulk \textbf{Delete}, \textbf{Cryptographically Hash}, \textbf{Encrypt} or \textbf{Decrypt} the user's Reddit posts or comments for better Privacy and Security
\begin{itemize}[leftmargin=1.5em]
    \item Used \textbf{Python} with \textbf{\praw} to develop the \textbf{4 features} in the script.
    \item Used \textbf{SHA-256}, \textbf{AES-Encryption} for privacy related features, ensuring reliable Hashing and Encryption of user data.
    \item Received \textbf{40+ Stars} on GitHub from the Open Source community.
\end{itemize}
\subsection*{NoNoise LinkedIn} \textit{\href{https://github.com/karan51ngh/no-noise-linkedin}{Source Code}} | \textit{\href{https://chromewebstore.google.com/detail/nonoise-linkedin/hbcjelfhlljdepmifggbmhnklhmdmldn}{Chrome Web Store Link}} \\
\textit{"NoNoise LinkedIn"} is an \textbf{Open Source} Chrome extension that removes \textbf{100\%} of the \textbf{"Suggested"} and \textbf{"Promoted"} posts, from the user's LinkedIn feed.
\begin{itemize}[leftmargin=1.5em]
    \item Utilized Vanilla \textbf{JavaScript} with \textbf{DOM Manipulation} and \textbf{JavaScript Events} along with \textbf{\href{https://developer.chrome.com/docs/extensions/reference/api}{Chrome extension APIs}} to create the extension.
    \item Achieved a \textbf{5-star} rating from \textbf{50+ users} and grew to \textbf{80+ active users} within the first month of launch on the Chrome Web Store, demonstrating strong user adoption and satisfaction.
\end{itemize}

% ========================
% \section*{\faGraduationCap\hspace{0.5em}Education and Research}
\section*{Education and Research}

\subsection*{B.Tech in Computer Science Engineering}
{Amrita School of Computing},  \\ \textit{Bangalore, 2019 -- 2023} 
\begin{itemize}[leftmargin=1.5em]
    \item Published 1 \textbf{Research Paper} titled \textit{"Proof-of-Trust-in-Expertise (PoTE): A Consensus Mechanism for Healthcare based Consortium Blockchains"} in Healthcare (\textit{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4804243}{Paper Link}}).
    \item Graduated with \textbf{First Class} with \textbf{Distinction} (8.2 CGPA) \textit{\href{https://drive.google.com/drive/folders/1Hu5mrXyz4nnYDJhT7x9IuLwLyBzCwkKB}{(Degree Certificate Link)}}.
    \item President at \textbf{CodeChef} - Amrita Bangalore Chapter for \textbf{1 year} and Technical Member at \textbf{Google DSC}, Amrita Bangalore for \textbf{3 years}.
\end{itemize}
\end{document}
